---
title: "A practical introduction to Shiny"
author: "Robin Lovelace (University of Leeds)"
date: "Presented 21^st^ January 2015, University of Sydney's ITLS"
logo: /home/robin/Dropbox/Public/img/logos/cdrc-square.png
output: ioslides_presentation
bibliography: /home/robin/Documents/R.bib
---

## What is shiny?

> - A framework for making R output **interactive**
> - An 'app' development framework
> - A (small) growing community of developers centred around RStudio

Similar projects you should be aware of before diving into Shiny

> - **animate** package
> - Google Charts (**googleVis::**)
> - **plotly**
> - D3

## What's shiny good for? | What's shiny not so good for?

Build's on R's existing strengths

> - Data visualisation [@wickham2011ggplot2]
> - Increasingline widely understood language for querying data
> - Amazing range of add-on packages

Flexibility


## Context

> - House of Commons Criticising the DfT for using closed models
> - 'Impact' and 'engagement' increasingly important for research funding
> - Complex data cannot be adequately summarised in a single static graphic
> - We've been contracted by the DfT (£100,000+) to create a 'propensity to cycle' tool

## Interactive online tools

> - AURIN
> - Leeds-Bradford cycle path
> - DECC's 'Energy 2050' planning tool
> - Walkability index site
> - Interactive download of bicycle paths

## Shiny applications

> - We'll take a look at a few online
> - Precision farming [[@Jahanshiri2014]](http://stacks.iop.org/1755-1315/20/i=1/a=012014)
> - Ebola app
> - Census wards app
> - RentSplit
> - No transport-related apps!

## Possible transport applications

> - Time tabling
> - Visualising flow data by mode/purpose/time
> - User engagement (e.g. of different scenarios)
> - Forms for questionnaires
> - Public outreach 

## The anatomy of a Shiny app

The **user interface** (`ui.R`)

```{r, eval=FALSE}
shinyUI(fluidPage(
))
```

The **server side** (`server.R`)

```{r, eval=FALSE}
shinyUI(fluidPage(
))
```

## The practical

> - Task 1: Modify RStudio's '01_hello' example
> - Task 2: Recreate **rentSplit**
> - Task 3: Create your own app!

## References




